Windowed least-squares model reduction for dynamical systems

### 2019-10-08 main.tex
working

\address[a]{Sandia National Laboratories,  Livermore, CA}
\begin{abstract}
This work proposes a \methodNameLower\ (\methodAcronym) model-reduction
	formulation for dynamical systems. The proposed approach sequentially minimizes the
	time-continuous full-order-model residual over a low-dimensional space--time trial
	subspace defined over an arbitrarily defined time window. The approach comprises a generalization 
of existing model reduction approaches, as particular instances of
  the methodology recover the Galerkin,
	least-squares Petrov--Galerkin (LSPG), and space–time LSPG approaches. In
	addition, the approach
	addresses key deficiencies in existing model-reduction
	techniques, e.g., the dependence of (space--time) LSPG on the
	time discretization and the exponential growth in time exhibited by \textit{a posteriori}
	error bounds for both Galerkin and LSPG.  We consider two types of
	space--time trial
	subspaces within the proposed framework: one that reduces only the spatial
	dimension of the full-order model, and one that reduces both the spatial and
	temporal dimensions of the full-order model.  For each type of trial
	subspace, we consider two different solution techniques: direct (i.e.,
	discretize-then-optimize) and indirect (i.e., optimize-then-discretize).
	Numerical experiments conducted using the trial subspaces characterized by spatial
	dimension reduction demonstrate that the \methodAcronym\
	approach can yield more accurate solutions that better satisfy the governing equations than
	the Galerkin and LSPG approaches.

@@

However, LSPG has several notable shortcomings. First, LSPG
exhibits a complex dependence on the time discretization. In
particular, changing
the time step modifies both the
time window over which LSPG minimizes the residual as well as the
time-discretization error of the full-order model on which LSPG is based. 
In particular, because LSPG and Galerkin are equivalent in the
limit as the time step goes to zero, the accuracy of LSPG approaches the (poor)
accuracy of Galerkin as the time step shrinks, but this also has the effect of
reducing the time-dicretization error of the full-order model.
As a
consequence, LSPG often yields the smallest error for an intermediate value of the
time step (see, e.g., Ref.~\cite[Figure 9]{carlberg_lspg_v_galerkin}); there
is no known way to compute this optimal time step \textit{a priori}.
Second, as the LSPG approach performs sequential residual minimization in
time, its \textit{a posteriori} error bounds grow exponentially in time
\cite{carlberg_lspg_v_galerkin}, and it is not equipped with any notion of
optimality over the entire time domain of interest. As a result, LSPG is not
equipped with \textit{a priori} guarantees of accuracy or stability, even for
linear time-invariant systems~\cite{bui_thesis}.

Researchers have pursued the development of space--time
residual-minimization approaches~\cite{choi_stlspg,constantine_strom,URBAN2012203,Yano2014ASC} to
address the issues incurred by sequential residual minimization in time.
Space--time residual-minimization approaches compute the space--time
trajectory within a low-dimensional space--time trial subspace (spanned by
a small number of space--time basis vectors) that minimizes the full-order-model
residual over the entire time domain.
We note that space--time residual minimization yields a fundamentlaly
different model than sequential residual minimization in time. In particular, space--time
residual minimization associates with an algebraic system of equations defined
over all space and time, whose solution comprises a \text{fixed} vector of
(space--time) generalized coordinates; on the other hand, sequential residual
minimization in time (often) associates with a system of ODEs whose solution
comprises a \textit{time-dependent} vector of (spatial) generalized
coordinates.
As a result, space--time residual minimization yields models that are equipped with \textit{a priori} error bounds that grow more slowly
in time, and the resulting \textit{trajectory} exhibits a notion of
optimality; this implies that the solution exhibits a notion of optimality
over the entire time domain. 
\EP{Come back to this, this also has to do with residual minimization}
However, these techniques also suffer from several
limitations. First, the computational cost of solving the algebraic system arising from space--time
approaches scales cubically with the number of space--time degrees of freedom;
in contrast, the computational cost incurred by standard
spatial-projection-based ROMs is linear in the number of temporal degrees of
freedom, as the attendant solvers can leverage the lower-block triangular
structure of the system arising from the sequential nature of time
evolution. As a result, solving the algebraic systems arising from space--time
projection is generally intractable without applying hyper-reduction in time
\cite{choi_stlspg,constantine_strom}. Second, space--time residual
minimization precludes future
state prediction, as these methods employ space--time basis vectors defined over the
entire time domain of interest, which must have been included in the training
simulations.

The objectives of this work are to overcome the shortcomings of existing
residual-minimizing methods, and to provide a unifying framework from which
existing methods can be assessed. In essence, the proposed  \textit{\methodNameLower\
(\methodAcronym)} method sequentially minimizes the FOM
residual over a sequence of arbitrarily defined
time windows. The method is characterized by three notable aspects.  First, the method
minimizes the \textit{time-continuous}  residual (i.e., that associated with
the full-order model ODE). By adopting a time-continuous viewpoint, the
formulation decouples the underlying temporal discretization scheme from the
residual-minimization problem, thus addressing a key deficiency of both LSPG
and space--time LSPG. Critically, time-continuous residual minimization also exposes
two different solution methods:  a \textit{discretize-then-optimize}
(i.e., direct) method, and an \textit{optimize-then-discretize} (i.e.,
indirect) method. Second, the method sequentially minimizes
the residual over arbitrarily defined \textit{time windows} rather than
sequentially minimizing the residual over time steps (as in LSPG)
or over the entire time domain (as in space--time residual-minimization
methods). This equips the method with additionally flexibility that enables it
to explore more fine-grained tradeoffs between computational cost and error.
Finally, \methodAcronym\ is formulated for two kinds of space--time trial
subspaces: one that reduces only the spatial dimension of the full-order
model (as employed by traditional spatial-projection-based methods), and one that reduces both the spatial and temporal dimensions of the
full-order model (as employed by space--time methods).
The above attributes allow that \methodAcronym\ method to be viewed as a
generalization of existing model-reduction methods, as 
Galerkin, LSPG, and space--time LSPG correspond to specific
instances of the formulation.
Figure~\ref{fig:flowchart} depicts how the proposed \methodAcronym\ method
provides a unifying framework from which these existing approaches can be derived.

The \methodAcronym\ approach can be viewed as a hybrid space--time method and displays 
commonalities with several related efforts. 
First, Ref.~\cite{bui_thesis} briefly formulated a space--time least-squares ROM
and connected this formulation with optimal control; specifically it mentioned the
optimize-then-discretize vs.\ discretize-then-optimize approaches. This work
did not fully develop this approach, eschewing it 
for 
sequential residual minimization in time (i.e., LSPG). The present work thus
formally develops and extends several of the concepts put forth
in Ref.~\cite{bui_thesis}. Next, Ref.~\cite{constantine_strom} developed a
space--time residual minimization formulation for model interpolation.  The
present work distinguishes itself from Ref.~\cite{constantine_strom} in that
(1) this work also considers trial subspaces characterized by a reduction of
the spatial dimension of the FOM only, and (2) we
minimize the time-continuous FOM residual over arbitrary time
windows. We note that,
similar to the current work, Ref.~\cite{constantine_strom} employs
minimization of the time-continuous FOM residual as a starting point; as such,
this work shares some thematic similarities with
Ref.~\cite{constantine_strom}.  Lastly, Ref.~\cite{choi_stlspg} develops a
space--time extension of the LSPG approach that minimizes the time-discrete
FOM residual over the entire time domain.  The present work distinguishes
itself from Ref.~\cite{choi_stlspg} in that (1) this work minimizes the
time-continuous FOM residual, (2) this work minimizes this residual over
arbitrary time windows, and (3) this work also considers trial subspaces
characterized by a reduction of the spatial dimension of the FOM only.

\begin{figure} 
\begin{centering} 
\includegraphics[trim={0.1cm 0cm 1cm 0cm},clip,width=0.99\textwidth]{diagram.pdf} 
\caption{Relationship diagram for the \methodAcronym\ framework for model
	reduction. \KTC{Inconsistent capitalization. I recommend using (1)
	``Limiting case'', (2) Space--time LSPG. Also, can we make this more specific? In particular, can
	we write specific equations (e.g., ``$W = T$ in Eq.~(10)'') for the limiting
	cases?}} 
\label{fig:flowchart} 
\end{centering} 
\end{figure}

 In summary, specific contributions of this work include:
\begin{enumerate}
%\item The development of a time-continuous residual minimization framework for reduced-order models.
\item The \methodNameLower\ (\methodAcronym) framework for dynamical-system
	model reduction. The approach sequentially minimizes the time-continuous
		full-order model residual over arbitrary time windows.
\item Support of two space--time trial subspaces: one that reduces the spatial
	dimension of the FOM only, and one that reduces both the spatial and
		temporal dimensions of the FOM. The former case is of particular
		interest in the \methodAcronym\  contex, as the stationary conditions are
		derived via the Euler--Lagrange equations and comprise a coupled two-point
		Hamiltonian boundary value problem containing a forward and backward
		system. The forward system, which is forced by an auxiliary costate,
		evolves the (spatial) generalized coordinates of the ROM in time. The
		backward system, which is forced by the time-continuous FOM residual
		evaluated about the ROM state, governs the dynamics of the costate. 
	\item Derivation of two solution techniques:
		\textit{discretize-then-optimize} (i.e., direct) and
		\textit{optimize-then-discretize} (i.e., indirect). 
	\item Derivations of conditions under which the
		\methodAcronym\ framework recovers Galerkin, LSPG, and space--time LSPG.
\item Error analysis of the \methodAcronym\ framework using
	trial subspaces characterized by a reduction of
the spatial dimension of the FOM only.
	This analysis demonstrates that, over a given window, the \methodAcronymROMs\ error 
		is bounded \textit{a priori} by a combination of the
		error at the start of the window and the integrated FOM ODE residual
		evaluated at the FOM state projected onto the trial subspace. 
\EP{Updated this, I don't show what you said}%As a result,
%		the error bound exhibits exponential growth in the number of time windows
%		(not total time instances), yielding smaller error-bound growth in thime than
%		Galerkin or LSPG projection. \KTC{Check this}
\item Numerical experiments for 
	trial subspaces characterized by a reduction of
the spatial dimension of the FOM only, which demonstrate two key findings:
\begin{itemize}
\item Minimizing the residual over a larger time window leads to more stable solutions 
with lower space--time residuals norms.
\item Minimizing the residual over a larger time window does not necessarily
	lead to a more accurate trajectory (as measured in the space--time
		$\elltwo$-norm of the solution). Instead, minimizing the residual over an
		intermediate-sized time window leads to the smallest trajectory error.
\end{itemize}
\end{enumerate}

The paper proceeds as follows: Section~\ref{sec:math}
outlines the mathematical setting for the full-order model, along with the Galerkin, LSPG, and
space--time LSPG approaches. Section~\ref{sec:tclspg} outlines the proposed \methodAcronym\
framework. Section~\ref{sec:numerical_techniques}
outlines numerical techniques for solving \methodAcronymROMs, including both direct and
indirect methods. Section~\ref{sec:analysis} provides
equivalence conditions and error analysis for \methodAcronymROMs.
Section~\ref{sec:numerical_experiments} presents numerical experiments.
Section~\ref{sec:conclude} provides conclusions and perspectives.
We denote vector-valued functions with italicized bold symbols (e.g., $\boldsymbol
x$), vectors with standard bold symbols (e.g., $\mathbf{x}$), 
matrices with capital bold symbols (e.g., $\mathbf{X} \equiv \begin{bmatrix}
\mathbf{x}_1 & \cdots & \mathbf{x}_r\end{bmatrix}$), and spaces with
calligraphic symbols (e.g., $\mathcal{X}$). We additionally denote differentiation of a time-dependent 
function with respect to with the $\dot\ $ operator.
%Model reduction of nonlinear dynamical systems is a growing research area.
%The least-squares Petrov-Galerkin (LSPG) approach has gained popularity as a model reduction technique for nonlinear dynamical systems. Derived at the fully discrete level, the LSPG approach solves a least-squares problem that minimizes the fully discrete residual of the reduced-order model at each time-step. LSPG has been shown to be an effective formulation for nonlinear model reduction on complex problems of interest.
%\begin{comment} 
\section{Mathematical formulation}\label{sec:math}
	We begin by providing the formulation for the full-order model,
	followed by a description of standard model-reduction methods
	classified according to the type of trial subspace they employ.
	\subsection{Full-order model}\label{sec;FOM}
We consider the full-order model to be a dynamical system expressed as a
	system of ordinary differential equations (ODEs)
\begin{equation}\label{eq:FOM}
 \stateFOMDotArg{t}  = \velocity(\stateFOMArg{}{t},t), \qquad \stateFOM(0) =
	\stateFOMIC,\qquad t \in [0,T]
\end{equation}
where  $\stateFOM: [0,T]
	\rightarrow  \RR{\fomdim}$ with $\stateFOM: \timeDummy \mapsto
	\stateFOM(\timeDummy) $ and $\stateFOMDot \equiv {d \stateFOM}/{d\tau}$
	denotes the state implicitly defined as the solution to initial value
	problem~\eqref{eq:FOM}, 
$T \in \mathbb{R}^+$ denotes the final time, 
 $\stateFOMIC \in \mathbb{R}^{\fomdim}$ denotes the initial condition,
	and $\velocity: \mathbb{R}^{\fomdim} \times [0,T] \rightarrow
	\mathbb{R}^{\fomdim}$ with $(\stateyDiscrete,\timeDummy) \mapsto
	\velocity(\stateyDiscrete,\timeDummy)$ denotes the velocity, which is possibly
	nonlinear in its first argument. For subsequent exposition, we introduce
	$\timeSpace$ to denote the set of real-valued functions acting on the time
	domain (i.e., $\timeSpace = \{f\,|\,f:[0,T]\rightarrow\RR{}\}$); the
	state can be expressed equivalently as $\stateFOM \in \RR{\fomdim} \otimes
	\timeSpace $.  We refer to the initial value problem defined in
	Eq.~\eqref{eq:FOM} as the ``full-order model" (FOM) ODE. We note that
	although the problem of interest described in the introduction corresponds
	to a parameterized dynamical system, we suppress dependence of the FOM ODE
	\eqref{eq:FOM} on such parameters for notational convenience, as this work
	focuses on devising a model-reduction approach applicable to a specific parameter instance.

@@

\subsection{Reduced-order models}
Projection-based ROMs generate approximate solutions to the FOM
	ODE~\eqref{eq:FOM} by approximating the state in a low-dimensional trial
	subspace. Two types of space--time trial subspaces are commonly used for
	this purpose: 
\begin{enumerate} 
	\item \textit{Subspaces that reduce only the spatial dimension of the full-order
		model (\spatialAcronym)}. These 
	trial subspaces are commonly used
		in model-reduction methods based on spatial projection followed by time
		integration (e.g., the Galerkin and LSPG approaches).
	\item \textit{Subspaces that reduce both the spatial and temporal dimensions of the full-order
		model (\spaceTimeAcronym)}. These trial subspaces are commonly employed in
		model-reduction methods based on space--time projection (e.g., space--time
		LSPG).
\end{enumerate}
 We now describe these two types of space--time trial subspaces and their
	application to the Galerkin, LSPG, and space--time LSPG approaches.

>>>>

\address[a]{Sandia National Laboratories,  Livermore, CA}
\begin{abstract}
This work proposes a \methodNameLower\ (\methodAcronym) approach for model-reduction
	of dynamical systems. The proposed approach sequentially minimizes the
	time-continuous full-order-model residual within a low-dimensional space--time trial
	subspace over time windows. The approach comprises a generalization 
of existing model reduction approaches, as particular instances of
  the methodology recover the Galerkin,
	least-squares Petrov--Galerkin (LSPG), and space–time LSPG approaches. In
	addition, the approach
	addresses key deficiencies in existing model-reduction
	techniques, e.g., the dependence of the (space--time) LSPG approach on the
	time discretization and the exponential growth in time exhibited by \textit{a posteriori}
	error bounds for both the Galerkin and LSPG approaches.  We consider two types of
	space--time trial
	subspaces within the proposed approach: one that associates with spatial projection only, and one that 
  associates with space--time projection. For each type of trial
	subspace, we consider two different solution techniques: direct (i.e.,
	discretize-then-optimize) and indirect (i.e., optimize-then-discretize).
	Numerical experiments conducted using trial subspaces characterized by spatial
	projection only demonstrate that the \methodAcronym\
	approach can yield more accurate solutions with lower space--time residuals than
	the Galerkin and LSPG approaches.

@@

However, LSPG has several notable shortcomings. First, LSPG
exhibits a complex dependence on the time discretization. In
particular, changing
the time step ($\Delta t$) modifies both the
time window over which LSPG minimizes the residual as well as the
time-discretization error of the full-order model on which LSPG is based. 
As LSPG and Galerkin are equivalent in the
limit of $\Delta t \rightarrow 0$, the accuracy of LSPG approaches the (sometimes poor)
accuracy of Galerkin as the time step shrinks.
For too-large a time step the accuracy of LSPG also degrades. It is unclear if this is due to the time-discretization error associated with enlarging the time step, or rather if it is due to the size of the window the residual is being minimized over.
% but this also has the effect of
%reducing the time-dicretization error of the full-order model.
As a
consequence, LSPG often yields the smallest error for an intermediate value of the
time step (see, e.g., Ref.~\cite[Figure 9]{carlberg_lspg_v_galerkin}); there
is no known way to compute this optimal time step \textit{a priori}.
Second, as the LSPG approach performs sequential residual minimization in
time, its \textit{a posteriori} error bounds grow exponentially in time
\cite{carlberg_lspg_v_galerkin}, and it is not equipped with any notion of
optimality over the entire time domain of interest. As a result, LSPG is not
equipped with \textit{a priori} guarantees of accuracy or stability, even for
linear time-invariant systems~\cite{bui_thesis}.

Researchers have pursued the development of space--time
residual-minimization approaches~\cite{choi_stlspg,constantine_strom,URBAN2012203,Yano2014ASC} to
address the issues incurred by sequential residual minimization in time.
Existing space--time approaches differ from the classic LSPG and Galerkin approaches in (1) the definition of the space--time trial subspace and (2) the definition of the residual minimization problem. First, space--time approaches leverage a space--time trial 
subspace that associates with a space--time projection; classic ``spatial" model reduction approaches such as LSPG and Galerkin leverage a space--time trial subspace that can be associated with spatial projection only. Second, space--time residual minimization approaches compute the entire space--time trajectory of the state (within the low-dimensional space--time trial subspace) that minimizes the full-order-model residual over the entire time domain; Galerkin and LSPG sequentially compute instances of the state that either minimize the full-order model instantaneously (Galerkin) or over a time-step instance (LSPG). 
The result of these differences is that space--time approaches yield an algebraic system of equations defined
over all space and time, whose solution comprises a \text{fixed} vector of
(space--time) generalized coordinates; on the other hand, spatial projection only approaches 
generally associates with a system of ODEs whose solution
comprises a \textit{time-dependent} vector of (spatial) generalized
coordinates.

%Space--time residual-minimization approaches compute the space--time
%trajectory within a low-dimensional space--time trial trial space that associates with space--time projection (spanned by
%a small number of space--time basis vectors) that minimizes the full-order-model
%residual over the entire time domain.
%We note that methods leveraging a trial subspace that associates with space--time 
%projection yields a fundamentally different model than methods that leverage a trial subspace that 
%associates with spatial projection only; in particular space--time
%projection associates with an algebraic system of equations defined
%over all space and time, whose solution comprises a \text{fixed} vector of
%(space--time) generalized coordinates; on the other hand, spatial projection only  
%generally associates with a system of ODEs whose solution
%comprises a \textit{time-dependent} vector of (spatial) generalized
%coordinates.
%We note that space--time residual minimization yields a fundamentlaly
%different model than sequential residual minimization in time. In particular, space--time
%residual minimization associates with an algebraic system of equations defined
%over all space and time, whose solution comprises a \text{fixed} vector of
%(space--time) generalized coordinates; on the other hand, sequential residual
%minimization in time (often) associates with a system of ODEs whose solution
%comprises a \textit{time-dependent} vector of (spatial) generalized
%coordinates.

Space--time residual minimization approaches minimize the FOM residual over all of space and time and, as a result, yield models that are equipped with a notion of space--time optimality and \textit{a priori} error bounds that grow more slowly
in time.
% and the resulting \textit{trajectory} exhibits a notion of
%optimality; this implies that the solution exhibits a notion of optimality
%over the entire time domain. 
%\EP{Come back to this, this also has to do with residual minimization}
However, these techniques also suffer from several
limitations. First, the computational cost of solving the algebraic system arising from space--time
approaches scales cubically with the number of space--time degrees of freedom;
in contrast, the computational cost incurred by standard
spatial-projection-based ROMs is linear in the number of temporal degrees of
freedom, as the attendant solvers can leverage the lower-block triangular
structure of the system arising from the sequential nature of time
evolution. As a result, solving the algebraic systems arising from space--time
projection is generally intractable without applying hyper-reduction in time
\cite{choi_stlspg,constantine_strom}. Second, space--time residual
minimization precludes future
state prediction, as these methods employ space--time basis vectors defined over the
entire time domain of interest, which must have been included in the training
simulations.

The objectives of this work are to overcome the shortcomings of existing
residual-minimizing methods, and to provide a unifying framework from which
existing methods can be assessed. In essence, the proposed  \textit{\methodNameLower\
(\methodAcronym)} method sequentially minimizes the FOM
residual over a sequence of arbitrarily defined
time windows. The method is characterized by three notable aspects.  First, the method
minimizes the \textit{time-continuous}  residual (i.e., that associated with
the full-order model ODE). By adopting a time-continuous viewpoint, the
formulation decouples the underlying temporal discretization scheme from the
residual-minimization problem, thus addressing a key deficiency of both LSPG
and space--time LSPG. Critically, time-continuous residual minimization also exposes
two different solution methods:  a \textit{discretize-then-optimize}
(i.e., direct) method, and an \textit{optimize-then-discretize} (i.e.,
indirect) method. Second, the method sequentially minimizes
the residual over arbitrarily defined \textit{time windows} rather than
sequentially minimizing the residual over time steps (as in LSPG)
or over the entire time domain (as in space--time residual-minimization
methods). This equips the method with additionally flexibility that enables it
to explore more fine-grained tradeoffs between computational cost and error.
Finally, \methodAcronym\ is formulated for two kinds of space--time trial
subspaces: one that associates with spatial projection only (as employed by traditional spatial-projection-based methods), and one that associates with space--time projection (as employed by space--time methods).
The above attributes allow the \methodAcronym\ approach to be viewed as a
generalization of existing model-reduction methods, as 
Galerkin, LSPG, and space--time LSPG correspond to specific
instances of the formulation.
Figure~\ref{fig:flowchart} depicts how the proposed \methodAcronym\ method
provides a unifying framework from which these existing approaches can be derived.

The \methodAcronym\ approach can be viewed as a hybrid space--time method and displays 
commonalities with several related efforts. 
First, Ref.~\cite{bui_thesis} briefly formulated a space--time least-squares ROM
and connected this formulation with optimal control; specifically it mentioned the
optimize-then-discretize vs.\ discretize-then-optimize approaches. This work
did not fully develop this approach, eschewing it 
for 
sequential residual minimization in time (i.e., LSPG). The present work thus
formally develops and extends several of the concepts put forth
in Ref.~\cite{bui_thesis}. Next, Ref.~\cite{constantine_strom} developed a
space--time residual minimization formulation for model interpolation.  The
present work distinguishes itself from Ref.~\cite{constantine_strom} in that
(1) this work also considers trial subspaces characterized by spatial projection only, and (2) we
minimize the time-continuous FOM residual over arbitrary time
windows. We note that,
similar to the current work, Ref.~\cite{constantine_strom} employs
minimization of the time-continuous FOM residual as a starting point; as such,
this work shares some thematic similarities with
Ref.~\cite{constantine_strom}.  Lastly, Ref.~\cite{choi_stlspg} develops a
space--time extension of the LSPG approach that minimizes the time-discrete
FOM residual over the entire time domain.  The present work distinguishes
itself from Ref.~\cite{choi_stlspg} in that (1) this work minimizes the
time-continuous FOM residual, (2) this work minimizes this residual over
arbitrary time windows, and (3) this work also considers trial subspaces
associated with spatial projection only.

\begin{figure} 
\begin{centering} 
\includegraphics[trim={0.1cm 0cm 1cm 0cm},clip,width=0.99\textwidth]{diagram.pdf} 
\caption{Relationship diagram for the \methodAcronym\ approach for model
	reduction. \KTC{Inconsistent capitalization. I recommend using (1)
	``Limiting case'', (2) Space--time LSPG. Also, can we make this more specific? In particular, can
	we write specific equations (e.g., ``$W = T$ in Eq.~(10)'') for the limiting
	cases?}} 
\label{fig:flowchart} 
\end{centering} 
\end{figure}

 In summary, specific contributions of this work include:
\begin{enumerate}
%\item The development of a time-continuous residual minimization framework for reduced-order models.
\item The \methodNameLower\ (\methodAcronym) approach for dynamical-system
	model reduction. The approach sequentially minimizes the time-continuous
		full-order model residual over arbitrary time windows.
%\item Support of two space--time trial subspaces: one that reduces the spatial
%	dimension of the FOM only, and one that reduces both the spatial and
%		temporal dimensions of the FOM. 
\item Support of two space--time trial subspaces: one that associates with spatial projection only and 
    one that associates with space--time projection.
The former case is of particular
		interest in the \methodAcronym\  contex, as the stationary conditions are
		derived via the Euler--Lagrange equations and comprise a coupled two-point
		Hamiltonian boundary value problem containing a forward and backward
		system. The forward system, which is forced by an auxiliary costate,
		evolves the (spatial) generalized coordinates of the ROM in time. The
		backward system, which is forced by the time-continuous FOM residual
		evaluated about the ROM state, governs the dynamics of the costate. 
	\item Derivation of two solution techniques:
		\textit{discretize-then-optimize} (i.e., direct) and
		\textit{optimize-then-discretize} (i.e., indirect). 
	\item Remarks and derivations of conditions under which the
		\methodAcronym\ approach recovers Galerkin, LSPG, and space--time LSPG.
\item Error analysis of the \methodAcronym\ approach using
	trial subspaces associated with spatial projection.
	This analysis demonstrates that, over a given window, the \methodAcronymROMs\ error 
		is bounded \textit{a priori} by a combination of the
		error at the start of the window and the integrated FOM ODE residual
		evaluated at the FOM state projected onto the trial subspace. 
\EP{Updated this, I don't show what you said}%As a result,
%		the error bound exhibits exponential growth in the number of time windows
%		(not total time instances), yielding smaller error-bound growth in thime than
%		Galerkin or LSPG projection. \KTC{Check this}
\item Numerical experiments for 
	trial subspaces associated with spatial projection only, which demonstrate two key findings:
\begin{itemize}
\item Minimizing the residual over a larger time window leads to more stable solutions 
with lower space--time residuals norms.
\item Minimizing the residual over a larger time window does not necessarily
	lead to a more accurate trajectory (as measured in the space--time
		$\elltwo$-norm of the solution). Instead, minimizing the residual over an
		intermediate-sized time window leads to the smallest trajectory error.
\end{itemize}
\end{enumerate}

The paper proceeds as follows: Section~\ref{sec:math}
outlines the mathematical setting for the full-order model, along with the Galerkin, LSPG, and
space--time LSPG approaches. Section~\ref{sec:tclspg} outlines the proposed \methodAcronym\
approach. Section~\ref{sec:numerical_techniques}
outlines numerical techniques for solving \methodAcronymROMs, including both direct and
indirect methods. Section~\ref{sec:analysis} provides
equivalence conditions and error analysis for \methodAcronymROMs.
Section~\ref{sec:numerical_experiments} presents numerical experiments.
Section~\ref{sec:conclude} provides conclusions and perspectives.
We denote vector-valued functions with italicized bold symbols (e.g., $\boldsymbol
x$), vectors with standard bold symbols (e.g., $\mathbf{x}$), 
matrices with capital bold symbols (e.g., $\mathbf{X} \equiv \begin{bmatrix}
\mathbf{x}_1 & \cdots & \mathbf{x}_r\end{bmatrix}$), and spaces with
calligraphic symbols (e.g., $\mathcal{X}$). We additionally denote differentiation of a time-dependent 
function with respect to with the $\dot\ $ operator.
%Model reduction of nonlinear dynamical systems is a growing research area.
%The least-squares Petrov-Galerkin (LSPG) approach has gained popularity as a model reduction technique for nonlinear dynamical systems. Derived at the fully discrete level, the LSPG approach solves a least-squares problem that minimizes the fully discrete residual of the reduced-order model at each time-step. LSPG has been shown to be an effective formulation for nonlinear model reduction on complex problems of interest.
%\begin{comment} 
\section{Mathematical formulation}\label{sec:math}
	We begin by providing the formulation for the full-order model,
	followed by a description of standard model-reduction methods
	classified according to the type of trial subspace they employ.
	\subsection{Full-order model}\label{sec;FOM}
We consider the full-order model to be a dynamical system expressed as a
	system of ordinary differential equations (ODEs)
\begin{equation}\label{eq:FOM}
 \stateFOMDotArg{t}  = \velocity(\stateFOMArg{}{t},t), \qquad \stateFOM(0) =
	\stateFOMIC,\qquad t \in [0,T]
\end{equation}
where  $\stateFOM: [0,T]
	\rightarrow  \RR{\fomdim}$ with $\stateFOM: \timeDummy \mapsto
	\stateFOM(\timeDummy) $ and $\stateFOMDot \equiv {d \stateFOM}/{d\tau}$
	denotes the state implicitly defined as the solution to initial value
	problem~\eqref{eq:FOM}, 
$T \in \mathbb{R}^+$ denotes the final time, 
 $\stateFOMIC \in \mathbb{R}^{\fomdim}$ denotes the initial condition,
	and $\velocity: \mathbb{R}^{\fomdim} \times [0,T] \rightarrow
	\mathbb{R}^{\fomdim}$ with $(\stateyDiscrete,\timeDummy) \mapsto
	\velocity(\stateyDiscrete,\timeDummy)$ denotes the velocity, which is possibly
	nonlinear in its first argument. For subsequent exposition, we introduce
	$\timeSpace$ to denote the set of real-valued functions acting on the time
	domain (i.e., $\timeSpace = \{f\,|\,f:[0,T]\rightarrow\RR{}\}$); the
	state can be expressed equivalently as $\stateFOM \in \RR{\fomdim} \otimes
	\timeSpace $.  We refer to the initial value problem defined in
	Eq.~\eqref{eq:FOM} as the ``full-order model" (FOM) ODE. We note that
	although the problem of interest described in the introduction corresponds
	to a parameterized dynamical system, we suppress dependence of the FOM ODE
	\eqref{eq:FOM} on such parameters for notational convenience, as this work
	focuses on devising a model-reduction approach applicable to a specific parameter instance.

@@

\subsection{Reduced-order models}
Projection-based ROMs generate approximate solutions to the FOM
	ODE~\eqref{eq:FOM} by approximating the state in a low-dimensional trial
	subspace. Two types of space--time trial subspaces are commonly used for
	this purpose: 
\begin{enumerate} 
	\item \textit{Subspaces that reduce only the spatial dimension of the full-order
		model (\spatialAcronym)}. These trial spaces are characterized by a \textit{spatial projection} process and are employed in classic model reduction approaches, e.g., Galerkin and LSPG. %These 
%	trial subspaces are commonly used
%		in model-reduction methods based on spatial projection followed by time
%		integration (e.g., the Galerkin and LSPG approaches).
	\item \textit{Subspaces that reduce both the spatial and temporal dimensions of the full-order
		model (\spaceTimeAcronym)}. 
 These trial subspaces are commonly employed in
		model-reduction methods based on space--time projection (e.g., space--time
		LSPG).
\end{enumerate}
 We now describe these two types of space--time trial subspaces and their
	application to the Galerkin, LSPG, and space--time LSPG approaches.
